---
title: "PWFSLSmoke practice"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(MazamaSpatialUtils)
library(PWFSLSmoke)
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(zoo)
library(knitr)
jv_palette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
```


```{r}
dir.create('~/Data/Spatial', recursive=TRUE)
setSpatialDataDir('~/Data/Spatial')
installSpatialData()
```

A first example

Let’s say we are interested in the impact of smoke from the 2018 Camp Fire on the Sacramento area.

We would begin by creating a camp_fire ws_monitor object that has all the monitors in California for the period of interest:

```{r}
camp_fire <- monitor_loadAnnual(2018) %>%
  monitor_subset(stateCodes = 'CA') %>%
  monitor_subset(tlim = c(20181108,20181123))
```

We can display these monitors (colored by maximum PM2.5 value) in an interactive map, zoom in and click on the monitor in downtown Sacramento to get it’s monitorID:

```{r}
monitor_leaflet(camp_fire)
```

We can use this monitorID to create a ws_monitor object for this single monitor and take a look at a timeseries plot:

```{r}
Sacramento <- camp_fire %>%
  monitor_subset(monitorIDs = '060670010_01')

monitor_timeseriesPlot(
  Sacramento,
  style='aqidots',
  pch=16,
  xlab="2018"
)
addAQIStackedBar()
addAQILines()
addAQILegend(cex=0.8)
title("Sacramento Smoke")
```

Next, we can use this specific location to create a ws_monitor object containing all monitors within 50km of Sacramento:

```{r}
Sacramento_area <-
  camp_fire %>%
  monitor_subsetByDistance(
    longitude = Sacramento$meta$longitude,
    latitude = Sacramento$meta$latitude,
    radius = 50
  )

monitor_leaflet(Sacramento_area)
```

We can display the hourly data for all the monitors and add day/night shading:

```{r}
monitor_timeseriesPlot(Sacramento_area, 
                       style='gnats',
                       shadedNight = TRUE)
```

We can average together all the monitors and create a local-time daily average for the Sacramento area:

```{r}
Sacramento_area %>%
  monitor_collapse() %>%
  monitor_dailyStatistic() %>%
  monitor_extractData()
```

Alternatively, we can plot the daily averages:

```{r}
Sacramento_area %>%
  monitor_collapse() %>%
  monitor_dailyBarplot(labels_x_nudge = 0.5,
                       labels_y_nudge = 15)
```



